HMM Model development

### 2020-05-15 dev/hmm_model_devel.Rmd
Making the HMM family more compatible with brms

>>>>

prepdata <- make_data_hmm(data$observed$formula, 
                              serie_data = data$observed$serie_data, 
                              rate_data = data$observed$rate_data, 
                              hidden_state_data = data$observed$hidden_state_data, 
                              initial_states = data$observed$initial_states,
                              observed_state_data = data$observed$observed_state_data,
                              sensitivity_low_bound = data$observed$sensitivity_low_bound)

bfit <- brm(formula = make_brms_formula_hmm(data$observed$formula), family = rate_hmm_family, data = prepdata$brmsdata, prior = data$observed$prior, stanvars = rate_hmm_stanvars(prepdata$standata))

bfit <- brms:::brmsfit(formula = make_brms_formula_hmm(data$observed$formula), data = prepdata$brmsdata, prior = data$observed$prior, stanvars = rate_hmm_stanvars(prepdata$standata), fit = fit)

bfit

posterior_epred(bfit)

brms::make_standata(formula = make_brms_formula_hmm(data$observed$formula), family = rate_hmm_family, data = prepdata$brmsdata, prior = data$observed$prior, stanvars = rate_hmm_stanvars(prepdata$standata))
